---
title: "02-copilot-complete"
format: html
---

Github Copilot was the first "Copilot", and that name was later absorbed by Microsoft. It is an AI model trained on all the data on Github, and it does come [with some controversy](https://en.wikipedia.org/wiki/GitHub_Copilot#Licensing_controversy).

Github Copilot of free for students who are authenticated through their program. That program evolves along with everything else in AI. On the day I write this in March 2026, Github is changing the structure, but the result is the same. 

[Read more here](https://docs.posit.co/ide/user/ide/guide/tools/copilot.html) about how to connect to you Github account.

Within RStudio, Copilot acts as a code completion tool. One effective way to use it is to descibe what you want to do within your notebook and then activate it.

## Scrape cfbstats web page

My goal here is to scrape the most recent page of Scoring Offence [from this page](https://cfbstats.com/2025/leader/national/team/offense/split01/category09/sort01.html) on cfbstats.

The questions I might ask Copilot

- What packages do I need to do this
- Scrape the table that has the scoring offense.
- Create a function where I can choose which year to scrape.

## The process I used

What packages do I need to start with?

```{r}
#| label: copilot-scrape
# what packages do I need?

library(rvest)
library(tidyverse)
```

Scrape the pages.

```{r}
#| label: copilot-scrape2

url <- "https://cfbstats.com/2025/leader/national/team/offense/split01/category09/sort01.html"

page <- read_html(url)

# pull the table of stats
stats_table <- page |> html_element("table") |> html_table()

# and then view it
stats_table
```

I will need to get different years. Write a function that allows me to enter a year into the function to grab those stats.

```{r}
#| label: copilot-scrape3

get_stats <- function(year) {
  url <- glue::glue("https://cfbstats.com/{year}/leader/national/team/offense/split01/category09/sort01.html")
  
  page <- read_html(url)
  
  stats_table <- page |> html_element("table") |> html_table()
  
  return(stats_table)
}

get_stats("2024")
get_stats("2023")
```






